### 2018-08-08 paper/evaluation.tex
more eval

Finally, the experiments had a timeout of 15 minutes. 
We observed that downloads---however big---usually succeeded long before this time, or did not succeed whatever time was given to them.

@@

@@

The experiments were conducted as follows: 
\begin{itemize}
  \item A first initialization procedure takes care of bootstrapping the users and their devices. 
  A scheduler is started for each user, that will turn devices on or off throughout the experiment according to the models discussed in~\ref{ssub:simulating_user_behavior};
  \item The 12 file exchanges are initiated in turn: a couple $(d_s, d_r)$ of online devices from different users is chosen.
  The sender $d_s$ is requested to initialize file upload
\end{itemize}

@@

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=0.8\columnwidth]{figures/completion_vs_size.pdf}

  \caption{\label{fig:completion_vs_size}
  Success rate of the file transfer ordered by size of file.}
\end{figure}

>>>>

Finally, the experiments had a timeout \texp of 15 minutes. 
We observed that downloads---however big---usually succeeded long before this time, or did not succeed whatever time was given to them.

@@

The experiments are conducted as follows: 
\begin{itemize}
  \item A first initialization procedure takes care of bootstrapping the users and their devices. 
  A scheduler is started for each user, that will turn devices on or off throughout the experiment according to the models discussed in~\ref{ssub:simulating_user_behavior};
  \item Each file is initiated in turn: a couple $(d_s, d_r)$ of online devices from different users is chosen.
  The sender $d_s$ is requested to initialize file upload---chunks hashes and routes take some time to compute---and answers with \finfo, including reply headers. 
  \finfo is given to $d_r$ as it is asked to receive $f$. It replies with forward headers, that are given to $d_s$. The exchange starts;
  \item We wait for this initialization process to end before starting to send the next file;
  \item Once all 12 files are initiated; we wait for the \texp timeout, unless all files have successfully completed their transfer, 
  in which case we early abort. This process takes up to a minute.
\end{itemize}

@@

Figure~\ref{fig:bw_and_pending_files} reads the timeline of a typical experiment by showing, 
in gray, the number of simultaneous file exchanges and, in black, the average outbound traffic per node per second.
The initialization phase is not part of the graph. 
In this particular experiment, all files were successfully exchanged.

We see that file transfers get started in turn, but that some complete fast, such that the maximum number of simultaneous downloads only rises to 8.
It quickly drops to 4 at 160s, but the last files take another 300s to finish. 
Those last files are either the biggest ones, or are exchanged between poorly connected nodes that tend not to be online at the same time.

The dark plot shows that the traffic is uneven, with frequent spikes in the MB/s order. 
The traffic is obviously dependent on the number of pending exchanges, 
but remains around 600 kB/s on average, even when 8 files are concurrently downloading.
Knowing that a chunk message weighs 516 kB, we deduce that nodes exchange an average of one chunk per second when the traffic is substantial.
We also see that the traffic remains non-null long after the last file finished downloading it. 
Indeed, some stale messages can remain in the buffers of poorly connected devices for an unbounded period of time.
This experiment finished early aborting past 600s.

@@

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=0.9\columnwidth]{figures/completion_vs_size.pdf}

  \caption{\label{fig:completion_vs_size}
  Success rate of the file transfer ordered by size of file over 30 experiments.
  The dotted black line shows the overall success rate of 94.4\%.}
\end{figure}

### 2018-08-08 paper/squad-overlay-design.tex
more eval

\paragraph*{Out-of-band initialization} 
When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
plus one reply header per chunk (as was seen in section~\ref{sec:SPOR}), and sends the whole to Bob.
Still out-of-band, Bob replies with one forward header per chunk.
This way, each chunk $\chunk_i$ is associated with a unique route both ways: 
a forward header $\forwardheader_i$ known by Alice, and a backward header $\backwardheader_i$ known by Bob.

>>>>

\paragraph*{Out-of-band initialization} 
When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
including one reply header per chunk (as was seen in section~\ref{sec:SPOR}), and sends the whole to Bob.
Still out-of-band, Bob replies with one forward header per chunk.
This way, each chunk $\chunk_i$ is associated with a unique route both ways: 
a forward header $\forwardheader_i$ known by Alice, and a backward header $\backwardheader_i$ known by Bob.
